---
title: "DV_RProject2"
author: "Monica and Rachel"
date: "September 28, 2015"
output: html_document
---  

```{r, include=FALSE}
require(tidyr)
require(dplyr)
require(ggplot2)
require (jsonlite)
require (RCurl)
```  

##**Part 1**
For our project, we extracted data concerning general information of hospitals in the United States. 
The code that we used to extract, transform, and load the data into an sql statement is as follows: 
```{r eval=FALSE}
source("../01 Data/ETL.R")
```
##**Part 2**
We imported the CVS file into a table in SQL.  
Then, we used the code below to display a subset of data for hospitals in Travis County, Texas. 
```{r, eval=FALSE}
source ("../01 Data/Titanic Analysis.R", echo = TRUE)
```
##**Part 3**
Lastly, we used data wrangling to create three interesting data sets that showed interesting trends. 
  
####**Data Set 1**  
For this data set we looked at all of the different types of hospitals across all of the states to get a good basis for our further analysis. We grouped by State, Hospital ownsership and hospital type. We used the summarize n() function to get totals for each category.   
```{r}
source("../02 Data Wrangling/Set 1.R", echo = TRUE)
```  
  
This data set shows us some interesting data that leads to the next data wrangling set. Veterans and childrens hospitals both have much lower numbers than any of the other hospital types across all of the states.  

####**Data Set 2**  
For this data set, we were interested in focusing on childrens hospitals as they it was one of the smallest groups of hospitals. We filtered by childrens hospital and then grouped by state. The points were colored by ownership type.  
```{r}
source("../02 Data Wrangling/Set 2.R", echo = TRUE)
```  
The results were actually pretty interesting. Out of 22 childrens hospitals only 1 of them was government owned. This is pretty fascinating considering how many hospitals were in this data set. Not only were so few of them childrens hospitals, but only 1 was government owned. Most were voluntary and non-profit. This says something about our healthcare system and the way it is politicized around making money.  
  
####**Data Set 3**
For this data set, we focused on states that had less than 20 emergencies. We then broke those states up even more and compared states that had less than 10 emergencies with states that had more than 10 emergencies in consideration with the type of hospital ownership.
```{r}
source("../02 Data Wrangling/Set 3.R", echo = TRUE)
```
We discovered that the states that had less than 5 emergencies were the American Samoa, the District of Columbia, Delaware, Guam, the Northern Mariana Islands, and the Virgin Islands. We noticed that all of these states are smaller and more obscure than the rest of the United States, and there may be less emergencies for many reasons, including lack of resources or reporting of emergencies. We also noticed that government owned hospitals tended to have even less emergencies than voluntary or proprietary hospitals.
